\hlc[green]{Uranyl Solvation by a Three-Dimensional Reference Interaction Site Model}

### 2015-06-17 doc/uo2_paper/uo2-II.tex
AM: changes by BL sent out on Jun 16th

\title{Uranyl solvation by a three-dimensional reference interaction site
model}
\author{Alexei Matveev}
\email{alexei.matveev@gmail.com}
\author{Bo Li}
\author{Notker Rösch}
\email{roesch@mytum.de}
\affiliation{Department Chemie, Technische Universität München, 85747 Garching,
Germany}
\alsoaffiliation{Catalysis Research Center, Technische Universität München, 85747
Garching, Germany}
\alsoaffiliation{Institute of High Performance Computing, Agency for Science, Technology
and Research, 1 Fusionopolis Way, Connexis \#16-16, Singapore 138632,
Singapore}
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

@@

The free energy calculations were carried out for the temperature
298~K, with the dielectric constant of bulk water set to 78.4, and
the solvent particle density $\rho=0.0333295$~Å$^{-3}$. These parameters
correspond to a pressure of 1~atm. The 3D domain was represented
by a cubic cell of $20^{3}$~Å$^{3}$ and a Cartesian grid with 96$^{3}$
points and a resolution of about 0.208~Å. The radial grid used to
precompute and interpolate the solvent susceptibility and its contractions
with the Coulomb kernel for use in Eq.~\ref{eq:tau} was chosen with
a radial range of 40~Å and 1536 points corresponding to a resolution
of about 0.026~Å. With these parameters, starting from scratch, a
calculation of the solvent susceptibility, the solvation energy, and
the corresponding forces for uranyl with six explicit water ligands
takes about 40 seconds on 8 cores of two Intel$^{\circledR}$ Xeon$^{\circledR}$
E5630 @ 2.53~GHz CPUs, where one achieves a parallel efficiency above
40\%. \hlc[green]{With the same computing power, a comparable 1D-RISM calculation takes about 10 seconds.} The non-linear solver converges in 8 iterations with about 380
Jacobian applications.

@@

\begin{figure}[tbph]
\caption{Radial distribution functions of solvated uranyl without explicit
aqua ligands: U--O$_{\text{w}}$ (top panel, black), U--H$_{\text{w}}$
(top panel, gray), O--O$_{\text{w}}$ (bottom panel, black) and O--H$\text{\ensuremath{_{w}}}$
(bottom panel, gray). Results obtained with the PSE1 closure are shown
as thick lines in the foreground, results obtained with the closure
relations PSE2 and PSE3 are displayed in the background using thinner
lines.  \label{fig:rdfs-vs-closure-0w}}

@@

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3 (solid lines of decreasing weight). The dashed line
represents the MD result of Ref.~\citenum{Bo15}.
\label{fig:potential-of-mean-force}}

>>>>

\title{\hlc[green]{Uranyl Solvation by a Three-Dimensional Reference Interaction Site
Model}}
\author{Alexei Matveev}
\email{alexei.matveev@gmail.com}
\author{Bo Li}
\author{Notker Rösch}
\email{roesch@mytum.de}
\affiliation{Department Chemie, Technische Universität München, 85747 Garching,
Germany}
\alsoaffiliation{Catalysis Research Center, Technische Universität München, 85747
Garching, Germany}
\alsoaffiliation{Institute of High Performance Computing, Agency for Science, Technology
and Research, 1 Fusionopolis Way, Connexis \#16-16, Singapore 138632,
Singapore}
%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}

@@

The free energy calculations were carried out for the temperature
298~K, with the dielectric constant of bulk water set to 78.4, and
the solvent particle density $\rho=0.0333295$~Å$^{-3}$. These parameters
correspond to a pressure of 1~atm. The 3D domain was represented
by a cubic cell of $20^{3}$~Å$^{3}$ and a Cartesian grid with 96$^{3}$
points and a resolution of about 0.208~Å. The radial grid used to
precompute and interpolate the solvent susceptibility and its contractions
with the Coulomb kernel for use in Eq.~\ref{eq:tau} was chosen with
a radial range of 40~Å and 1536 points corresponding to a resolution
of about 0.026~Å. With these parameters, starting from scratch, a
calculation of the solvent susceptibility, the solvation energy, and
the corresponding forces for uranyl with six explicit water ligands
takes about 40 seconds on 8 cores of two Intel$^{\circledR}$ Xeon$^{\circledR}$
E5630 @ 2.53~GHz CPUs, where one achieves a parallel efficiency above
40\%. \hlc[green]{With the same computing equipment, a comparable 1D-RISM calculation takes about 10 seconds.} The non-linear solver converges in 8 iterations with about 380
Jacobian applications.

@@

\begin{figure}[tbph]
\caption{Radial distribution functions of solvated uranyl without explicit
aqua ligands: U--O$_{\text{w}}$ (top panel, \hlc[green]{red}), U--H$_{\text{w}}$
(top panel, \hlc[green]{blue}), O--O$_{\text{w}}$ (bottom panel, \hlc[green]{red}) and O--H$\text{\ensuremath{_{w}}}$ (bottom panel, \hlc[green]{blue}). Results obtained with the PSE1 closure are shown
as \hlc[green]{solid lines}, results obtained with the closure relations PSE2 and PSE3 are displayed \hlc[green]{using dashed lines and dotted lines respectively}.  \label{fig:rdfs-vs-closure-0w}}

@@

\begin{figure}[tbph]
\begin{centering}
\caption{Potential of mean force, $W(r)$, from the U--O$_{\text{w}}$ radial
distribution function, determined with the closure relations PSE1,
PSE2 and PSE3, \hlc[green]{are displayed as solid, dashed and dot-dashed lines respectively}. The \hlc[green]{dotted} line
represents the MD result of Ref.~\citenum{Bo15}.
\label{fig:potential-of-mean-force}}
